19Q1

### 2019-05-20 19Q1.Rmd

```{r g2p}
g2p <- read.delim("./data_munging/g2p_db_edited.csv", sep = ",", header = TRUE)

g2p_dgls <-  as.character(unique(g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)]))
g2p_druggenes <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
```

>>>>

```{r g2p}
g2p <- read.delim("./data_munging/g2p_db_edited.csv", sep = ",", header = TRUE)
g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", g2p$biomarker_type_curated)

g2p_dgls <-  as.character(unique(g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)]))
g2p_druggenes <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))

g2p_split <- split(g2p, g2p$biomarker_type_curated)
g2p_amp <- g2p_split[[1]]
```
